---
title: "Hitters"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prerequisites


```{r}
# Helper packages
library(recipes)   # for feature engineering
library(tidyverse) # general data munging

# Modeling packages
library(glmnet)   # for implementing regularized regression
library(caret)    # for automating the tuning process
library(rsample)  # for sampling

# Model interpretability packages
library(vip)      # for variable importance


```

#Quistion 1
*Using the Hitters dataset from the ISLR package (data(Hitters, package = "ISLR")):
```{r}
# ames data
Hitters
data(Hitters, package = "ISLR")
# initial dimension
dim(Hitters)

# response variable
head(Hitters$Salary)

#Delete NA
Hitters <- na.omit(Hitters)

# split data
set.seed(123)
split <- initial_split(Hitters, strata = "Salary",prop = 0.7)
hitters_train <- training(split)

```
#Quistion 2
*Apply a ridge model with glmnet with Salary being the response variable.

```{r}
# Create training  feature matrices
# we use model.matrix(...)[, -1] to discard the intercept
X <- model.matrix(Salary ~ ., hitters_train)[, -1]

# transform y with log transformation
Y <- log(hitters_train$Salary)

#Ridge
ridge <- glmnet(
  x = X,
  y = Y,
  alpha = 0
)

plot(ridge, xvar = "lambda")



#Ridge CV model:
plot(lasso, xvar = "lambda")

ridge <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 0
)

```
*What is the minimum MSE?
*What is the minimum MSE within 1 standard error?
*What are the lambda values for these MSEs?
```{r}
# Ridge model - minimum MSE
min(ridge$cvm)

# Ridge model - lambda for this min MSE
ridge$lambda.min 

# Ridge model w/1-SE rule
ridge$cvm[ridge$lambda == ridge$lambda.1se]

# Ridge model w/1-SE rule -- No. of coef | 1-SE MSE
ridge$nzero[ridge$lambda == ridge$lambda.1se]
```

#Quistion 3
*Apply a lasso model with glmnet.

```{r}
#Lasso

lasso <- glmnet(
  x = X,
  y = Y,
  alpha = 1
)


#Lasso CV model:
plot(ridge)

lasso <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 1
)

plot(lasso)
```
*What is the minimum MSE?
*What is the minimum MSE within 1 standard error?
*What are the lambda values for these MSEs?
```{r}
# Lasso model - minimum MSE
min(lasso$cvm)       

# Lasso model - lambda for this min MSE
lasso$lambda.min 

# Lasso model - w/1-SE rule
lasso$cvm[lasso$lambda == lasso$lambda.1se]

# Lasso model w/1-SE rule -- No. of coef | 1-SE MSE
lasso$nzero[lasso$lambda == lasso$lambda.1se]
```

#Quistion 4
*Perform a grid search across alpha parameter values ranging between 0–1.
*How does it compare to your previous models?
```{r}
# tuning grid
hyper_grid <- expand.grid(
  alpha = seq(0, 1, by = .25),
  lambda = c(0.1, 10, 100, 1000, 10000)
)

# perform resampling
set.seed(123)
cv_glmnet <- train(
  x = X,
  y = Y,
  method = "glmnet",
  preProc = c("zv", "center", "scale"),
  trControl = trainControl(method = "cv", number = 10),
  tuneLength = 10
)

# best model
cv_glmnet$results %>%
  filter(
    alpha == cv_glmnet$bestTune$alpha,
    lambda == cv_glmnet$bestTune$lambda
    )

# plot results
plot(cv_glmnet)

# predict Salary on training data
pred <- predict(cv_glmnet, X)

# compute RMSE of transformed predicted
RMSE(exp(pred), exp(Y))
```


#Quistion 5
*Plot the top 10 most influential features. Do these features have positive or negative impacts on your response variable?

```{r prereqs-data}
vip(cv_glmnet, num_features = 20, geom = "point")
```
