---
title: "Food demands"
output: html_document
---

#About the data

Given the following information, the task is to predict the number of oreders for the next 10 weeks for the meal combinations, which are:

Historical data of demand for a product-center combination (Weeks: 1 to 145)
Product(Meal) features such as category, sub-category, current price and discount
Information for fulfillment centers like center area, city information, etc.

Taking from:
https://www.kaggle.com/gauravsahani/food-demand-prediction-dataset


#Data and libraries

```{r}
#package required
library(rsample)
library(tidyverse)
library(stats)
library(dplyr)
library(caret)

#data
food <- read.csv("Food_demand.csv")
# initial dimension
dim(food)

# response variable
head(food$num_orders)

```
##Data splitting and distribution.

```{r}
            
set.seed(123) # for reproducibility
split <- initial_split(food, strata = "num_orders", prop = 0.7)
food_train <- training(split)
food_test  <- testing(split)

#Model with lm()
```{r}
lm_food <- lm(num_orders ~., data = food_train)
summary(lm_food)

caret_food <- train(num_orders ~ ., data = food_train, 
                  method = "lm")
caret_food
```

