---
title: "AmesExercise"
output: html_document
---
#Data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Packages required
library(rsample)
library(caret)
library(tidyverse)
library(modeldata)
library(recipes)

# Data required
## ames data
ames <- AmesHousing::make_ames()

## attrition data
churn <- data(attrition)
```

#Quistion 1
*Rather than use a 70% stratified training split, try an 80% unstratified training split. How does your cross-validated results compare?
```{r}
set.seed(123)
split  <- initial_split(ames, prop = 0.8, strata = "Sale_Price")
ames_train  <- training(split)
ames_test   <- testing(split)
```


#Quistion 2
*Rather than numerically encode the quality and condition features (i.e. step_integer(matches("Qual|Cond|QC|Qu"))), one-hot encode these features. 
*What is the difference in the number of features your training set? 
*Apply the same cross-validated KNN model to this new feature set.
*How does the performance change? How does the training time change?

```{r}
# Original categories
count(ames_train, 'Qual|Cond|QC|Qu')

# Label encoded
encode <- recipe(Sale_Price ~ ., data = ames_train) %>%
  step_integer(matches("Qual|Cond|QC|Qu")) %>% 
  prep(ames_train) %>%
  bake(ames_train) %>%
  count("Qual|Cond|QC|Qu")
encode

# 3. create a resampling method
cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5
  )

# 4. create a hyperparameter grid search
hyper_grid <- expand.grid(k = seq(2, 25, by = 1))

# 5. execute grid search with knn model
#    use RMSE as preferred metric
knn_fit <- train(
  encode, 
  data = ames_train, 
  method = "knn", 
  trControl = cv, 
  tuneGrid = hyper_grid,
  metric = "RMSE"
  )
```


#Quistion 3
*Identify three new step_xxx functions that recipes provides:
*Why would these feature engineering steps be applicable to the Ames data?
*Apply these feature engineering steps along with the same cross-validated KNN model. How do your results change?

```{r}


```


#Quistion 4
*Using the Attrition data set, assess the characterstics of the target and features.
*Which target/feature engineering steps should be applied?
*Create a feature engineering blueprint and apply a KNN grid search. What is the performance of your model?

```{r}

```

