---
title: "Hitters"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prerequisites


```{r}
# Helper packages
library(recipes)   # for feature engineering
library(tidyverse) # general data munging
library(dplyr)     # for data wrangling
library(ggplot2)   # for awesome plotting
# Modeling packages
library(glmnet)   # for implementing regularized regression
library(caret)    # for automating the tuning process
library(rsample)  # for sampling
library(earth)     # for fitting MARS models

# Model interpretability packages
library(vip)      # for variable importance
library(pdp)       # for variable relationships
library(rsample)
```
```

#Quistion 1
*Using the Hitters dataset from the ISLR package (data(Hitters, package = "ISLR")):

```{r}
# hitters data
Hitters
data(Hitters, package = "ISLR")
# initial dimension
dim(Hitters)

# response variable
head(Hitters$Salary)

#Delete NA
Hitters <- na.omit(Hitters)

# split data
set.seed(123)
split <- initial_split(Hitters, strata = "Salary",prop = 0.7)
hitters_train <- training(split)

```
#Quistion 2
*Apply a ridge model with glmnet with Salary being the response variable.

```{r}
# Create training  feature matrices
# we use model.matrix(...)[, -1] to discard the intercept
X <- model.matrix(Salary ~ ., hitters_train)[, -1]

# transform y with log transformation
Y <- log(hitters_train$Salary)

#Ridge
ridge <- glmnet(
  x = X,
  y = Y,
  alpha = 0
)

plot(ridge, xvar = "lambda")



#Ridge CV model:
plot(lasso, xvar = "lambda")

ridge <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 0
)

```
*What is the minimum MSE?
*What is the minimum MSE within 1 standard error?
*What are the lambda values for these MSEs?
```{r}
# Ridge model - minimum MSE
min(ridge$cvm)

# Ridge model - lambda for this min MSE
ridge$lambda.min 

# Ridge model w/1-SE rule
ridge$cvm[ridge$lambda == ridge$lambda.1se]

# Ridge model w/1-SE rule -- No. of coef | 1-SE MSE
ridge$nzero[ridge$lambda == ridge$lambda.1se]
```

#Quistion 3
*Apply a lasso model with glmnet.

```{r}
#Lasso

lasso <- glmnet(
  x = X,
  y = Y,
  alpha = 1
)


#Lasso CV model:
plot(ridge)

lasso <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 1
)

plot(lasso)
```
*What is the minimum MSE?
*What is the minimum MSE within 1 standard error?
*What are the lambda values for these MSEs?
```{r}
# Lasso model - minimum MSE
min(lasso$cvm)       

# Lasso model - lambda for this min MSE
lasso$lambda.min 

# Lasso model - w/1-SE rule
lasso$cvm[lasso$lambda == lasso$lambda.1se]

# Lasso model w/1-SE rule -- No. of coef | 1-SE MSE
lasso$nzero[lasso$lambda == lasso$lambda.1se]
```

#Quistion 4
*Perform a grid search across alpha parameter values ranging between 0–1.
*How does it compare to your previous models?
```{r}
# tuning grid
hyper_grid <- expand.grid(
  alpha = seq(0, 1, by = .25),
  lambda = c(0.1, 10, 100, 1000, 10000)
)

# perform resampling
set.seed(123)
cv_glmnet <- train(
  x = X,
  y = Y,
  method = "glmnet",
  preProc = c("zv", "center", "scale"),
  trControl = trainControl(method = "cv", number = 10),
  tuneLength = 10
)

# best model
cv_glmnet$results %>%
  filter(
    alpha == cv_glmnet$bestTune$alpha,
    lambda == cv_glmnet$bestTune$lambda
    )

# plot results
plot(cv_glmnet)

# predict Salary on training data
pred <- predict(cv_glmnet, X)

# compute RMSE of transformed predicted
RMSE(exp(pred), exp(Y))
```


#Quistion 5
*Plot the top 10 most influential features. Do these features have positive or negative impacts on your response variable?

```{r prereqs-data}
vip(cv_glmnet, num_features = 20, geom = "point")
```

#Quistion
*Apply a MARS model with all features.
*How does the model performance compare to your previous models?
```{r}
caret::getModelInfo("earth")$earth$parameters
```
```{r}
# Fit a basic MARS model
mars1 <- earth(
  Salary ~ .,  
  data = hitters_train   
)

# Print model summary
print(mars1)
```
*How many of the features are influential? Which 10 features are considered most influential?
```{r}
summary(mars1) %>% .$coefficients %>% head(10)
```

*Does your model include hinge functions? If so, explain their coefficient and plot their impact on the predicted response variable.

```{r cv-mars}
# tuning grid
hyper_grid <- expand.grid(
  nprune = seq(2, 50, length.out = 10) %>% floor(),
  degree = 1:3
)

# perform resampling
set.seed(123)
cv_mars <- train(
  Salary ~ ., 
  data = hitters_train, 
  trControl = trainControl(method = "cv", number = 10),
  method = "earth", #<<
  tuneGrid = hyper_grid,
  metric = "RMSE"
  )

# best model
cv_mars$results %>%
  filter(
    nprune == cv_mars$bestTune$nprune,
    degree == cv_mars$bestTune$degree
    )

# plot results
plot(cv_mars)
```



```{r}
# variable importance plots
p1 <- vip(cv_mars, num_features = 40, geom = "point", value = "gcv") + ggtitle("GCV")
p2 <- vip(cv_mars, num_features = 40, geom = "point", value = "rss") + ggtitle("RSS")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

*Does your model include interactions? If so, pick the interaction effect that is most influential and explain the coefficient.
```{r pdp, fig.width=15, fig.height=3, warning=FALSE, message=FALSE}
# Construct partial dependence plots
p1 <- partial(cv_mars, pred.var = "CRBI", grid.resolution = 10) %>% 
  ggplot(aes(CRBI, yhat)) +
  geom_line()

p2 <- partial(cv_mars, pred.var = "Years", grid.resolution = 10) %>% 
  ggplot(aes(Years, yhat)) +
  geom_line()
p3 <- partial(cv_mars, pred.var = c("CRBI", "Years"), 
              grid.resolution = 10) %>% 
  plotPartial(levelplot = FALSE, zlab = "yhat", drape = TRUE, colorkey = TRUE, 
              screen = list(z = -20, x = -60))
# Display plots side by side
gridExtra::grid.arrange(p1, p2, p3, ncol = 3)
```

