---
title: "Loan"
output: html_document
---

##Data Set Information:

This research aimed at the case of customers’ default payments in Taiwan and compares the predictive accuracy of probability of default among six data mining methods. From the perspective of risk management, the result of predictive accuracy of the estimated probability of default will be more valuable than the binary result of classification - credible or not credible clients

##Source:

Name: I-Cheng Yeh
email addresses: (1) icyeh '@' chu.edu.tw (2) 140910 '@' mail.tku.edu.tw
institutions: (1) Department of Information Management, Chung Hua University, Taiwan. (2) Department of Civil Engineering, Tamkang University, Taiwan.
other contact information: 886-2-26215656 ext. 3181
https://archive.ics.uci.edu/ml/datasets/default+of+credit+card+clients

```{r}
#Packages 
library(tidyverse)
library(ggplot2)
library(caret)
library(rsample)
library(recipes)

#Data
loan <- read.csv("UCI_Credit_Card.csv")

##I had this warning:You are trying to do regression and your outcome only has two possible values Are you trying to do classification? If so, use a 2 level factor as your outcome column##
# In order to avoid it I changes variables into factors .. but it didn't work
loan$default.payment.next.month =as.factor(loan$default.payment.next.month)
loan$SEX =as.factor(loan$SEX)
loan$MARRIAGE =as.factor(loan$MARRIAGE)
loan$EDUCATION =as.factor(loan$EDUCATION)
```

#Data 

```{r}
# initial dimension
dim(loan)
glimpse(loan)
head(loan$default.payment.next.month)
```
```{r}
#Work with sample
loan2 <- sample(loan, size = 700, replace = FALSE ) 

#Splitting the data
set.seed(123)
split <- initial_split(loan, strata = "default.payment.next.month", prop = 0.7)
loan_train <- training(split)
loan_test  <- testing(split)

```


```{r}
# Normalize to resolve numeric feature skewness and standardize (center and scale) numeric features
#Perform dimension reduction on numeric features.
recipe(default.payment.next.month ~ ., data = loan_train) %>%
  step_YeoJohnson(all_numeric()) %>% 
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes()) %>% 
  step_pca(all_numeric(), threshold = .95)
```

```{r}
#Filter out zero or near-zero variance features
caret::nearZeroVar(loan_train, saveMetrics = TRUE) %>% 
  tibble::rownames_to_column() %>% 
  filter(nzv)
```



```{r}

# create a resampling method
cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5
  )

# create a hyperparameter grid search
hyper_grid <- expand.grid(k = seq(2, 10, by = 100))


# execute grid search with knn model
# use RMSE as preferred metric
knn_fit <- train(
  default.payment.next.month ~ ., 
  data = loan_train, 
  method = "knn", 
  trControl = cv, 
  tuneGrid = hyper_grid,
  metric = "RMSE"
  )

# evaluate results
# print model results
knn_fit
```

```{r}
# plot cross validation results
ggplot(knn_fit$results, aes(k, RMSE)) + 
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = scales::dollar)

```


#apply simple linear regression model
```{r}

#LM
lm_loan1 <- lm(default.payment.next.month ~ LIMIT_BAL , data = loan_train)
summary(lm_loan1)

#Model concerns
coef(lm_loan1)

##why it doesn't work?
#Model Accuracy
set.seed(123)
cv_model1 <- train(
  default.payment.next.month ~ LIMIT_BAL ,
  data = loan_train, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)

```

```{r}
#apply simple linear regression model

lm_loan2 <- lm(default.payment.next.month ~ AGE , data = loan_train)
summary(lm_loan2)

#Model concerns
coef(lm_loan2)

#Model Accuracy
set.seed(123)
cv_lm_loan2 <- train(
  default.payment.next.month ~ AGE , data = loan_train, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)
```
```{r}
lm_loan3 <- lm(default.payment.next.month~ ., data = loan_train)
tidy(lm_loan3)

#Model concerns
coef(lm_loan3)

#Model Accuracy
set.seed(123)
(cv_lm_loan3 <- train(
  default.payment.next.month ~ ., data = loan_train, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10))
)
```

```{r}
# perform 10-fold cross validation on a PCR model tuning the 
# number of principal components to use as predictors from 1-100
set.seed(123)
cv_model_pcr <- train(
  default.payment.next.month~ .,
  data = loan_train, 
  method = "pcr",
  trControl = trainControl(method = "cv", number = 10),
  preProcess = c("zv", "center", "scale"),
  tuneLength = 100
  )
```


