---
title: "Obesity"
output: html_document
---

#Discribtion:

This dataset include data for the estimation of obesity levels in individuals from the countries of Mexico, Peru and Colombia, based on their eating habits and physical condition.

#Variables:
The data contains 17 attributes and 2111 records, the records are labeled with the class variable NObesity (Obesity Level), that allows classification of the data using the values of Insufficient Weight, Normal Weight, Overweight Level I, Overweight Level II, Obesity Type I, Obesity Type II and Obesity Type III. 77% of the data was generated synthetically using the Weka tool and the SMOTE filter, 23% of the data was collected directly from users through a web platform.


#sorce:
https://archive.ics.uci.edu/ml/datasets/Estimation+of+obesity+levels+based+on+eating+habits+and+physical+condition+


```{r}
#Packages 
library(tidyverse)
library(ggplot2)
library(caret)
library(rsample)
library(recipes)
library(broom) #for cross validation of glm
#library(magrittr)
#library(modelr)

#Data
obesity <- read.csv("ObesityDataSet_raw_and_data_sinthetic.csv")

#changes variables into factors
obesity$Gender =as.factor(obesity$Gender)
obesity$family_history_with_overweight=as.factor(obesity$family_history_with_overweight)
obesity$FAVC =as.factor(obesity$FAVC)
obesity$CAEC =as.factor(obesity$CAEC)
obesity$SMOKE =as.factor(obesity$SMOKE)
obesity$SCC =as.factor(obesity$SCC)
obesity$CALC =as.factor(obesity$CALC)
obesity$MTRANS =as.factor(obesity$MTRANS)
obesity$NObeyesdad =as.factor(obesity$NObeyesdad)
```


```{r}
# initial dimension
dim(obesity)
glimpse(obesity)
head(obesity$NObeyesdad)
```

#Splitting the data
```{r}
#Splitting the data by 70/30

set.seed(123)
split <- initial_split(obesity, strata = "NObeyesdad", prop = 0.7)
obesity_train <- training(split)
obesity_test  <- testing(split)

```

#Feature ingeneering

```{r}
# Normalize to resolve numeric feature skewness and standardize (center and scale) numeric features
recipe(NObeyesdad ~ ., data = obesity_train) %>%
  step_YeoJohnson(all_numeric()) %>% 
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes())
```




```{r}
#Filter out zero or near-zero variance features
caret::nearZeroVar(obesity_train, saveMetrics = TRUE) %>% 
  tibble::rownames_to_column() %>% 
  #should I remove?
  filter(nzv)
```

```{r}

#Perform dimension reduction on numeric features.
recipe(NObeyesdad ~ ., data = obesity_train) %>%
  step_center(all_numeric()) %>%
  step_scale(all_numeric()) %>%
  step_pca(all_numeric(), threshold = .95)
```

```{r}
# One-hot or dummy encode categorical features.

blueprint <- recipe(NObeyesdad ~ ., data = obesity_train) %>%
  step_nzv(all_nominal()) %>%
  step_integer(matches("Gender,family_history,FAVC,CAEC,SMOKE,SCC,
                       CALC,MTRANS,NObeyesdad")) %>% 
  step_dummy(all_nominal(), one_hot = TRUE)

summary(blueprint)
```


```{r}

#What is this doing and does the above enough?
# Label encoded 
 recipe(NObeyesdad ~ ., data = obesity_train) %>%
  step_integer(matches("Gender,family_history,FAVC,CAEC,SMOKE,SCC,CALC,MTRANS,NObeyesdad")) %>%
  prep(obesity_train) %>%
  bake(obesity_train)
```

#SVM model (polynomial kernal)
```{r}
#build training model
model <- train(NObeyesdad ~ ., data = obesity_train,
               method = "svmPoly",
               preProcess = c("scale","center"),
               trControl = trainControl(method = "none"),
               tuneGrid = data.frame(degree=1 , scale=1, C=1))
```

```{r}
#build cross validation model
cv <- train(NObeyesdad ~ ., data = obesity_train,
               method = "svmPoly",
               preProcess = c("scale","center"),
               trControl = trainControl(method = "cv", number = 10),
               tuneGrid = data.frame(degree=1 , scale=1, C=1))
```


```{r}
#Apply model for prediction
model_training <- predict(model, obesity_train)#apply model to predict training set
model_testing <- predict(model, obesity_test)#apply model to predict testing set
model_cv <- predict(cv, obesity_train)#preform cross validation
```

```{r}
#model performance(displays confusion matrix and statistics)
model_training_confusion <- confusionMatrix(model_training, obesity_train$NObeyesdad)
model_testing_confusion <- confusionMatrix(model_testing, obesity_test$NObeyesdad)
model_cv_confusion <- confusionMatrix(model_cv, obesity_train$NObeyesdad)
```

```{r}
model_testing_confusion
```


```{r}
model_training_confusion
```


```{r}
model_cv_confusion
```

```{r}
#feature importance 
importance <- varImp(model)

#plot shows the importance features of predicting each category
plot(importance)

```

#apply simple linear regression model
```{r}

#GLM
glm_obesity1 <-glm(NObeyesdad ~ Weight, data = obesity_train,family="binomial")
summary(glm_obesity1)

#Model concerns
coef(glm_obesity1)


##What should I replace "glm"?
#Model Accuracy
#set.seed(123)
#(cv_lm_obesity1 <- train(
 # NObeyesdad ~ Weight, data = obesity_train, 
  #method = "glm",
  #trControl = cv)
#)

  
# calculate predictions using validation set
obesity_test_accuracy <- augment(glm_obesity1, data = obesity_train,
                           type.predict = "response") %>% 
  mutate(pred = as.numeric(.fitted > .5))


# calculate test error rate
mean(obesity_test_accuracy$NObeyesdad != obesity_test_accuracy$pred, na.rm = TRUE)

```



```{r}
glm_obesity2 <- glm(NObeyesdad ~ family_history_with_overweight + Weight, data = obesity_train, family = "binomial")
summary(glm_obesity2)

#Model concerns
coef(glm_obesity2)

#Model Accuracy

set.seed(123)
(cv_glm_obesity2 <- train(
  NObeyesdad ~ Family_history_with_overweight,
  data = obesity_train, 
  method = "glm",
  trControl = cv)
)
```


```{r}
glm_obesity3 <- glm(NObeyesdad ~ ., data = obesity_train, family = "binomial")
summary(glm_obesity3)

#Model concerns
coef(glm_obesity3)

#Model Accuracy
set.seed(123)
(cv_glm_obesity3 <- train(
  NObeyesdad ~ ., data = obesity_train, 
  method = "glm",
  trControl = cv)
)

# calculate predictions using validation set
obesity_test_accuracy2 <- augment(glm_obesity3, data = obesity_train,
                           type.predict = "response") %>% 
  mutate(pred2 = as.numeric(.fitted > .5))


# calculate test error rate
mean(obesity_test_accuracy2$NObeyesdad != obesity_test_accuracy2$pred2, na.rm = TRUE)
```


